Batch Bayesian Optimization via Multi-objective Acquisition Ensemble for Automated Analog Circuit Design

### 2018-02-08 paper/background.tex
Paper update

% TODO: See how other people describe GP and BO}
In this section, we will present the problem formulation of analog circuit optimization, and review the background of Gaussian process regression and Bayesian optimization.

@@

% TODO: The circuit performance comes from \bf{circuit} simulation}
% TODO: format, citation of HSPICE/spectre}
% TODO: See how other analog circuit optimization paper formulate the problem}

We handle the scenarios where the topology of the analog circuit is fixed. This
is practical as there are usually a lot of classical topologies for given
design task. Once the circuit topology is fixed, the designer has to choose the
appropriate design parameters according to the specifications and the circuit
device model. What we want to do is automatically searching for the optimal
design parameters. This problem can then be formulated as a bound-constrained
black-box optimization problem:
\begin{equation}
    \label{eq:Formulation}
    \text{minimize}~\mathrm{FOM}(\bm{x}),
\end{equation}
where $\bm{x} \in \textrm{D}$ is the vector of design variables,
$\mathrm{FOM}(\bm{x})$ is the objective constructed from the design
specifications. Given the design parameters $\bm{x}$, the FOM value can be
obtained by commercial circuit simulators like HSPICE or Spectre.

% \textcolor{red}{TODO: If there is still space, illustrate the objecive with the PM-width figure}

% \begin{figure}[]
%     \begin{center}
%         \centerline{\includegraphics[width=\columnwidth]{./img/PM.eps}}
%         \caption{Phase margin of an amplifier as function of the width of a transistor}
%         \label{fig:PMOpAmp}
%     \end{center}
% \end{figure}

@@

\textcolor{red}{
    TODO:
    \begin{enumerate}
            \item Noise
            \item MLE learning
    \end{enumerate}
}

@@

Given a new data point $\bm{x}$, the prediction of $f(\bm{x})$ is
not a scalar value, but a predictive distribution
\begin{equation}
f(\bm{x}) \sim N(\mu(\bm{x}),
\sigma^2(\bm{x})),
\label{eq:GPRPred}
\end{equation}
where $\mu(\bm{x})$ and $\sigma^2(\bm{x})$ can be expressed as
\begin{equation}
        \begin{array}{lll}
            \mu(\bm{x}) &=& \mu_0 + k(\bm{x},X)K^{-1}(\bm{y} - \mu_0) \\
            \sigma^2(\bm{x}) &=&  - k(\bm{x}, X)K^{-1}k(X, \bm{x}),
        \end{array}
    \label{eq:GPRPredEqNoisy}
\end{equation}
where $k(\bm{x}, X) = (k(\bm{x}, \bm{x}_1), \dots, k(\bm{x},
\bm{x}_N))^T$ and $k(X, \bm{x}) = k(\bm{x}, X)^T$. The
$\mu(\bm{x})$ can be viewed as the prediction of the function value, while
the $\sigma^2(\bm{x})$ is a measure of uncertainty of the prediction. The hyperparameters including the parameters of the kernel function, and $\mu_0$ can be obtained by Maximum Likelihood Estimation (MLE) based on the training data set.

\textcolor{red}{$\sigma_f$ ???, it is not necessary to mention it here.}

@@

\textcolor{red}{TODO: Add Input, Output parameters}
\begin{algorithm}
\caption{Bayesian Optimization}
\label{alg:BayesianOptAlgo}
\begin{algorithmic}[1]
\STATE Initial Sampling
\STATE Construct initial GP model
\FOR{t = 1, 2, \dots}
\STATE Construct the acquisition function
\STATE Find $\bm{x}_t$ that optimizes the acquisition function
\STATE Sample $y_t = f(\bm{x}_t)$
\STATE Update probabilistic surrogate model
\ENDFOR
\STATE Return best $f(\bm{x})$ recorded during iterations
\end{algorithmic}
\end{algorithm}

>>>>

In this section, we will present the problem formulation of analog circuit optimization, and review the background of Gaussian process regression and Bayesian optimization.

@@

We handle the scenarios where the topology of the analog circuit is fixed. This
is practical as there are usually a lot of classical topologies for given
design task. Once the circuit topology is fixed, the designer has to choose the
appropriate design parameters according to the specifications and the circuit
device model. What we want to do is automatically searching for the optimal
design parameters. This problem can then be formulated as a bound-constrained
black-box optimization problem:
\begin{equation}
    \label{eq:Formulation}
    \text{minimize}~\mathrm{FOM}(\bm{x}),
\end{equation}
where $\bm{x} \in \textrm{D}$ is the vector of design variables,
$\mathrm{FOM}(\bm{x})$ is the objective constructed from the design
specifications, the $\mathrm{FOM}(\bm{x})$ can be deterministric of noisy
depending on the design specifications. Given the design parameters $\bm{x}$,
the FOM value can be obtained by commercial circuit simulators like HSPICE or
Spectre.

@@

% \textcolor{red}{
%     TODO:
%     \begin{enumerate}
%             \item Noise
%             \item MLE learning
%     \end{enumerate}
% }

@@

Given a new data point $\bm{x}$, the prediction of $f(\bm{x})$ is
not a scalar value, but a predictive distribution
\begin{equation}
f(\bm{x}) \sim N(\mu(\bm{x}),
\sigma^2(\bm{x})),
\label{eq:GPRPred}
\end{equation}
where $\mu(\bm{x})$ and $\sigma^2(\bm{x})$ can be expressed as
\begin{equation}
        \begin{array}{lll}
            \mu(\bm{x})      &=& \mu_0 + k(\bm{x},X)K^{-1}(\bm{y} - \mu_0) \\
            \sigma^2(\bm{x}) &=& k(\bm{x}, \bm{x}) - k(\bm{x}, X)K^{-1}k(X, \bm{x}),
        \end{array}
    \label{eq:GPRPredEqNoisy}
\end{equation}
where $k(\bm{x}, X) = (k(\bm{x}, \bm{x}_1), \dots, k(\bm{x},
\bm{x}_N))^T$ and $k(X, \bm{x}) = k(\bm{x}, X)^T$. The
$\mu(\bm{x})$ can be viewed as the prediction of the function value, while
the $\sigma^2(\bm{x})$ is a measure of uncertainty of the prediction. The hyperparameters including the parameters of the kernel function, and $\mu_0$ can be obtained by Maximum Likelihood Estimation (MLE) based on the training data set.

@@

\begin{algorithm}
    \caption{Bayesian Optimization}
    \label{alg:BayesianOptAlgo}
    \begin{algorithmic}[1]
        \REQUIRE Number of initial sampling points $N_{init}$, number of iterations $N_{iter}$
        \STATE Randomly sample $N_{init}$ points in the design space
        \STATE Construct initial GP model
        \FOR{t = 1, 2, \dots, $N_{iter}$}
        \STATE Construct the acquisition function
        \STATE Find $\bm{x}_t$ that optimizes the acquisition function
        \STATE Sample $y_t = f(\bm{x}_t)$
        \STATE Update probabilistic surrogate model
        \ENDFOR
        \STATE \textbf{Return} best $f(\bm{x})$ recorded during iterations
    \end{algorithmic}
\end{algorithm}
